Brownian Dynein Model

### 2015-10-27 latex/derivation.tex
Add work on derivation.tex X/Y_t derivatives.

  &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{Y_{fm}-Y_{nm}}{2L}\sqrt{\frac{4L_t^2}{\left(X_{fm}-X_{nm}\right)^2 + \left(Y_{fm}-Y_{nm}\right)^2} -1}\\

@@

   &\mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\left(\frac{\left(\frac{-4L_t^2\left(-2BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb}-\dot{\theta}_{nb})\right)}{\left(2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})\right)^2}\right)}{2\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}}\right)\\

@@

\subsection{$Y_t$}
\begin{align*}
  Y_t &= Y_{nm} + L_t\sin(\theta_1 \pm \theta_2)\\
  &= Y_{nm} + L_t\sin\left(\cos^{-1}\left(\frac{X_{fm}-X_{nm}}{L}\right) \pm \cos^{-1}\left(\frac{L}{2L_t}\right) \right)
  \hspace*{1in} \sin\Big(cos^{-1}(a)\pm cos^{-1}(b)\Big) = \sqrt{1-a^2}b\pm a\sqrt{1-b^2}\\
  &= Y_{nm} + L_t\left(\frac{L}{2L_t}\sqrt{1 - \frac{\left(X_{fm}-X_{nm}\right)^2}{L^2}} \pm \frac{X_{fm}-X_{nm}}{L}\sqrt{1 - \frac{L^2}{4L^2_t}}\right)\\
  &= Y_{nm} + \frac{L}{2}\sqrt{1 - \frac{\left(X_{fm}-X_{nm}\right)^2}{L^2}} \pm \frac{X_{fm}-X_{nm}}{2L}\sqrt{4L_t^2 - L^2}\\
  &= Y_{nm} + \frac{1}{2}\sqrt{L^2 - \left(X_{fm}-X_{nm}\right)^2} \pm \frac{X_{fm}-X_{nm}}{2}\sqrt{\frac{4L_t^2}{L^2} - 1}\\
  &= Y_{nm} + \frac{1}{2}\sqrt{\left(Y_{fm}-Y_{nm}\right)^2} \pm \frac{X_{fm}-X_{nm}}{2}\sqrt{\frac{4L_t^2}{\left(X_{fm}-X_{nm}\right)^2 + \left(Y_{fm}-Y_{nm}\right)^2} - 1}\\
  &= \frac{Y_{fm} + Y_{nm}}{2} \pm \frac{X_{fm}-X_{nm}}{2}\sqrt{\frac{4L_t^2}{\left(X_{fm}-X_{nm}\right)^2 + \left(Y_{fm}-Y_{nm}\right)^2} - 1}\\
  &= \frac{Y_{fm} + Y_{nm}}{2} \pm \frac{X_{fm}-X_{nm}}{2}\sqrt{\frac{4L_t^2}{X_{fm}^2 + X_{nm}^2 + Y_{fm}^2 + Y_{nm}^2 -2X_{fm}X_{nm} -2Y_{fm}Y_{nm}} - 1}\\
  &= \frac{L_s\sin(\theta_{fb}) + L_s\sin(\theta_{nb})}{2} \pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2} *\\
  &\sqrt{\frac{4L_t^2}{B^2 + L_s^2\cos^2(\theta_{fb}) + BL_s\cos(\theta_{fb}) + L_s^2\cos^2(\theta_{nb}) + L_s^2\sin^2(\theta_{fb}) + L_s^2\sin^2(\theta_{nb}) -2(B + L_s\cos(\theta_{fb}))L_s\cos(\theta_{nb}) -2L_s^2\sin(\theta_{fb})\sin(\theta_{nb})} - 1}\\\\
  &= \frac{L_s\sin(\theta_{fb}) + L_s\sin(\theta_{nb})}{2} \pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2} *\\
  &\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb})\cos(\theta_{nb}) - 2L_s^2\sin(\theta_{fb})\sin(\theta_{nb})} - 1}\\\\
  &= \frac{L_s\sin(\theta_{fb}) + L_s\sin(\theta_{nb})}{2} \pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}\\
\end{align*}

@@

\section{Cartesian Velocities}
This section shows the velocity definitions. \\
\begin{align}
  \dot{X}_{nb} &= 0 \\
  \dot{X}_{nm} &= -L_s\sin(\theta_{nb})\dot{\theta}_{nb}\\
  \dot{X}_{t } &= \frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} + -L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2} \mp \frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} - L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
  &\pm \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\frac{\frac{-4L_t^2}{\left(2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})\right)^2} \left(-2BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb}+\dot{\theta}_{nb})\right)}{2\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}}\\
  \dot{X}_{fm} &= -L_s\sin(\theta_{fb})\dot{\theta}_{fb}\\
  \dot{X}_{fb} &= 0
\end{align}

>>>>

  &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{Y_{fm}-Y_{nm}}{2}\sqrt{\frac{4L_t^2}{\left(X_{fm}-X_{nm}\right)^2 + \left(Y_{fm}-Y_{nm}\right)^2} -1}\\

@@

   \dot{X}_t &= \frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} - L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2} \mp \left(\frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} - L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2}\right)\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
   &\pm \frac{L_{t}^2\left(L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})\right)\left(-2BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb}-\dot{\theta}_{nb})\right)}{\left(2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})\right)^2\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}}\\

@@

\subsection{$Y_t$}
  Y_t &= Y_{nm} + L_t\sin(\theta_1 \pm \theta_2)\\
  &= Y_{nm} + L_t\sin\left(\cos^{-1}\left(\frac{X_{fm}-X_{nm}}{L}\right) \pm \cos^{-1}\left(\frac{L}{2L_t}\right) \right)
  \hspace*{1in} \sin\Big(cos^{-1}(a)\pm cos^{-1}(b)\Big) = \sqrt{1-a^2}b\pm a\sqrt{1-b^2}\\
  &= Y_{nm} + L_t\left(\frac{L}{2L_t}\sqrt{1 - \frac{\left(X_{fm}-X_{nm}\right)^2}{L^2}} \pm \frac{X_{fm}-X_{nm}}{L}\sqrt{1 - \frac{L^2}{4L^2_t}}\right)\\
  &= Y_{nm} + \frac{L}{2}\sqrt{1 - \frac{\left(X_{fm}-X_{nm}\right)^2}{L^2}} \pm \frac{X_{fm}-X_{nm}}{2L}\sqrt{4L_t^2 - L^2}\\
  &= Y_{nm} + \frac{1}{2}\sqrt{L^2 - \left(X_{fm}-X_{nm}\right)^2} \pm \frac{X_{fm}-X_{nm}}{2}\sqrt{\frac{4L_t^2}{L^2} - 1}\\
  &= Y_{nm} + \frac{1}{2}\sqrt{\left(Y_{fm}-Y_{nm}\right)^2} \pm \frac{X_{fm}-X_{nm}}{2}\sqrt{\frac{4L_t^2}{\left(X_{fm}-X_{nm}\right)^2 + \left(Y_{fm}-Y_{nm}\right)^2} - 1}\\
  &= \frac{Y_{fm} + Y_{nm}}{2} \pm \frac{X_{fm}-X_{nm}}{2}\sqrt{\frac{4L_t^2}{\left(X_{fm}-X_{nm}\right)^2 + \left(Y_{fm}-Y_{nm}\right)^2} - 1}\\
  &= \frac{Y_{fm} + Y_{nm}}{2} \pm \frac{X_{fm}-X_{nm}}{2}\sqrt{\frac{4L_t^2}{X_{fm}^2 + X_{nm}^2 + Y_{fm}^2 + Y_{nm}^2 -2X_{fm}X_{nm} -2Y_{fm}Y_{nm}} - 1}\\
  &= \frac{L_s\sin(\theta_{fb}) + L_s\sin(\theta_{nb})}{2} \pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2} *\\
  &\sqrt{\frac{4L_t^2}{B^2 + L_s^2\cos^2(\theta_{fb}) + 2BL_s\cos(\theta_{fb}) + L_s^2\cos^2(\theta_{nb}) + L_s^2\sin^2(\theta_{fb}) + L_s^2\sin^2(\theta_{nb}) -2(B + L_s\cos(\theta_{fb}))L_s\cos(\theta_{nb}) -2L_s^2\sin(\theta_{fb})\sin(\theta_{nb})} - 1}\\\\
  &= \frac{L_s\sin(\theta_{fb}) + L_s\sin(\theta_{nb})}{2} \pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2} *\\
  &\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb})\cos(\theta_{nb}) - 2L_s^2\sin(\theta_{fb})\sin(\theta_{nb})} - 1}\\\\
  &= \frac{L_s\sin(\theta_{fb}) + L_s\sin(\theta_{nb})}{2} \pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}\\
  \dot{Y}_t &= \frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} + L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2}\\
  &\pm \frac{d}{dt}\left(\frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2}\right)\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}\\
  &\pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2} \frac{d}{dt}\left(\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}\right)\\
  \dot{Y}_t &= \frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} + L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2}\\
  &\pm \left(\frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} + L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2}\right)\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}\\
  &\pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2} \left(\frac{\frac{-4L_t^2}{\left(2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})\right)^2}}{2\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}}\right)*\\
  &\left(-2BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb} - \dot{\theta}_{nb})\right)\\\\
  \dot{Y}_t &= \frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} + L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2} \pm \left(\frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} + L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2}\right)\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}\\
  &\mp \frac{L_t^2\left(B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})\right)\left(-2BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb} - \dot{\theta}_{nb})\right)}{\left(2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})\right)^2\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}}\\

@@

\section{Cartesian Velocities}
This section shows the velocity definitions. \\
\begin{align}
  \dot{X}_{nb} &= 0 \\
  \dot{X}_{nm} &= -L_s\sin(\theta_{nb})\dot{\theta}_{nb}\\
  \dot{X}_{t } &= \frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} - L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2} \mp \left(\frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} - L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2}\right)\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
   &\pm \frac{L_{t}^2\left(L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})\right)\left(-2BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb}-\dot{\theta}_{nb})\right)}{\left(2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})\right)^2\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}}\\
  \dot{X}_{fm} &= -L_s\sin(\theta_{fb})\dot{\theta}_{fb}\\
  \dot{X}_{fb} &= 0
\end{align}
